---
title: "Using the `powers` package"
author: "Alvin Qiu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for teaching purposes.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! Now, expanded with logarithm functions too!

```{r}
library(powers)
```

Sick of seeing `log2` or `log10` as the only option? Too lazy to specify a base? Now, we have `log3`, `log4` and `log5`!

```{r}
log3(1:10)
log4(1:10)
log5(1:10)
```


Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
```

Wow!!!
